---
title: "GEOG 3023: Statistics for Geography"
subtitle: "Final Project: Grading a professor "
author: Rigo Estrada
output: 
  html_document:
    css: "lab.css"


Goal : score rating based on attractiveness, what did you use, what plots, why did you choose those, what analysis allowed you to make statesments that are in your discussion. Methods: How you found it? What did you find, what was interesting, why might this score impact, give a fun hypotheses at start (guess if it will affect), fun hypotheses for why it impacted.


references:
- id: Hamermesh2005
  title: Beauty in the Classroom - Instructors' Pulchritude and Putative Pedagogical Productivity
  author:
  - family: Hamermesh
    given: Daniel S.
  - family: Parker
    given: Amy
  volume: 24
  URL: 'http://www.sciencedirect.com/science/article/pii/S0272775704001165'
  DOI: 10.1016/j.econedurev.2004.07.013
  publisher: Economics of Education Review
  ISSN: 0272-7757
  issue: 4
  page: 369-376
  type: article-journal
  issued:
    year: 2005
    month: 8
- id: Gelman2007
  title: Data Analysis Using Regression and Multilevel/Hierarchical Models
  author:
  - family: Gelman
    given: Andrew
  - family: Hill
    given: Jennifer
  publisher: Cambridge University Press
  city:
  type: book
  issued:
    year: 2007
  edition: 1
  ISBN: 9780521686891
---

<div class="instructions">

example:

model = lm(score~bty_avg, data=evals)
summary(model)
plot(score~bty_avg, data=evals)
**Logistics:**

Please complete the following project and submit the finished Rmd and HTML
file and a poster (a template is enclosed) about the project onto Canvas.

You have two weeks to work on the project, please return by the first week
of December (*December 1st* if you are in Wednesday lab, and *December 2nd*
if you are in Thursday lab). 

As mentioned in the class, you can work with
If you work in group, in
the poster and Rmd file, please clearly state which group member did which
part of the project.




**Requirements:**

Since this is a final project, you can choose any methods we have discussed
in the classes, but the methods to be used must include some of the
following elements:

- basic descriptive statistics (e.g., `cor()`, `mean()`, `sd()`)


- statistical plots (e.g., `hist()`, `boxplot()`, `qqplot()`, `scatterplot()`)


- hypothesis testing (e.g., `t.test()`, `wilcox.test()`, `ks.test()`) or confidence interval


- regression modeling (e.g., `lm()`) or AVOVA (e.g., `aov()`, `anova()`).

You must provide interpretations of the analysis results, and present your
results in the format of a poster (a template is enclosed). The post should
include the following four sections:

- Introduction
- Methods
- Results
- Discussion


**What to submit:**

- Rmd file
- Knitted html file
- Poster as described above

Lastly, don't forget to change name field in the beginning to your **first and last name**. 

If there is anything not clear, please contact Guofeng or Kylen. 

This project is modified based on [OpenIntro](https://www.openintro.org/stat/labs.php) lab.

</div>

## Grading a professor

Many college courses conclude by giving students the opportunity to
evaluate the course and the instructor anonymously. However, the use of
these student evaluations as an indicator of course quality and teaching
effectiveness is often criticized because these measures may reflect the
influence of non-teaching related characteristics, such as the physical
appearance of the instructor, rank, age and ethnicity. Foe example, the
article titled, "Beauty in the classroom: instructors' pulchritude and
putative pedagogical productivity" [@Hamermesh2005] found that instructors
who are viewed to be better looking receive higher instructional ratings.

The main idea of the project is to use the statistical methods we learned
in the class to help find what factors can go into a positive professor
evaluation.

### The data

The data were gathered from end of semester student evaluations for a large 
sample of professors from the University of Texas at Austin. In addition, six 
students rated the professors' physical appearance. (This is a based on the
original data set that was released as part of the replication 
data for *Data Analysis Using Regression and Multilevel/Hierarchical Models* 
[@Gelman2007].) The result is a data frame where each row contains a 
different course and columns represent variables about the courses and 
professors.

Let's load the data:

```{r load-data, message=FALSE}
evals<-read.csv('evals.csv')
```

variable         | description
---------------- | -----------
`score`          | average professor evaluation score: (1) very unsatisfactory - (5) excellent.
`rank`           | rank of professor: teaching, tenure track, tenured.
`ethnicity`      | ethnicity of professor: not minority, minority.
`gender`         | gender of professor: female, male.
`language`       | language of school where professor received education: english or non-english.
`age`            | age of professor.
`cls_perc_eval`  | percent of students in class who completed evaluation.
`cls_did_eval`   | number of students in class who completed evaluation.
`cls_students`   | total number of students in class.
`cls_level`      | class level: lower, upper.
`cls_profs`      | number of professors teaching sections in course in sample: single, multiple.
`cls_credits`    | number of credits of class: one credit (lab, PE, etc.), multi credit.
`bty_f1lower`    | beauty rating of professor from lower level female: (1) lowest - (10) highest.
`bty_f1upper`    | beauty rating of professor from upper level female: (1) lowest - (10) highest.
`bty_f2upper`    | beauty rating of professor from second upper level female: (1) lowest - (10) highest.
`bty_m1lower`    | beauty rating of professor from lower level male: (1) lowest - (10) highest.
`bty_m1upper`    | beauty rating of professor from upper level male: (1) lowest - (10) highest.
`bty_m2upper`    | beauty rating of professor from second upper level male: (1) lowest - (10) highest.
`bty_avg`        | average beauty rating of professor.
`pic_outfit`     | outfit of professor in picture: not formal, formal.
`pic_color`      | color of professor's picture: color, black & white.


### Load packages

As usual, load the packages that might be needed for the project. 

```{r load-packages, message=FALSE}
library(dplyr)
```

### Now start to work on the project



## References
